Supporting information: Copulas and their potential for ecology

### 2019-09-22 Paper.Rmd
a comment changed
copula abbreviation added in table caption

<!--***DAN: Notes on what needs to be done to this section, so far only getting up through the presentation of the bivariate results:
1) be more nuanced in the presentation, don't give the appearance of sweeping results that dont agree with the general conclusions under the rug
2) Add AIC and BIC columsn to table S3, and all analogous figures (e.g., S5, S7, S9, etc). Also reduce the number of digits shown after the decimal to 2 for AIC and BIC and 4 for the other columns.
3) Move Table S3 to an appropriate place in the main text. Choose the place based on where it is first cited in the main text.
4) Sort the rows of Table S2 (and all analogous tables) AIC, putting the lowest
AIC at the top. This should mean the highest AICw is at the top.
5) move some of the content from appendices S6 and S7 into methods, and move fig S21 and table S4 into main text. These are non-parametric results for
soil C and N. So we will be presenting the nonparam results more comprehensively in the main text.
6) That means you also need to summarize the nonparm results for the other 3 bivariate systems in Table 2. How to do this? Maybe put the cor results only, for Spearman only (or Kendall, not sure which to choose) into Table 2.  
7) Probably ought to combine tables S6, S8, S10 into one table, and fix it so
whenever we currently cite one of those, change it so we cite the combined table instead.
-->

@@

<!--Display model selection results for soilCN data in a table-->
```{r tab_soilCNfit, echo=F, results="asis"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
BivMS_res_Loecke<-readRDS("./Results/fitting_results/BivMS_soilCN.RDS")
h<-BivMS_res_Loecke$InfCritRes[,c("copname","AIC","AICw","BIC","BICw","LTdep","UTdep")]
colnames(h)<-c("copula","AIC","AICw","BIC","BICw","LT","UT")
h_ord <- h[order(h$AIC),] #sorting data: min AIC to max AIC
knitr::kable(h_ord, #longtable = T, 
             format = "latex",linesep = "",row.names = F, digits = c(4,2,2,2,2,4,4),
      caption.short = "Model fitting results for soil C and N dataset",
      caption = "Model fitting results for soil C and N dataset using 16 copula families: copula name abbreviations are given in the main text. AICw = AIC weight; BICw = BIC weight; LT = the lower-tail dependence statistic for the indicated copula family, with fitted parameters; UT = the same for upper-tail dependence. Wights and tail dependences are rounded upto 2 and 4 digits, respectively. \\label{tab_soilCNfit}",
      booktabs = TRUE)
```

>>>>

<!--***DAN: Notes on what needs to be done to this section, so far only getting up through the presentation of the bivariate results:
1) be more nuanced in the presentation, don't give the appearance of sweeping results that dont agree with the general conclusions under the rug
2) Add AIC and BIC columsn to table S3, and all analogous figures (e.g., S5, S7, S9, etc). Also reduce the number of digits shown after the decimal to 2 for AIC and BIC and 4 for the other columns.
3) Move Table S3 to an appropriate place in the main text. Choose the place based on where it is first cited in the main text.
4) Sort the rows of Table S2 (and all analogous tables) AIC, putting the lowest
AIC at the top. This should mean the highest AICw is at the top.
5) move some of the content from appendices S6 and S7 into methods, and move fig S21 and table S4 into main text. These are non-parametric results for
soil C and N. So we will be presenting the nonparam results more comprehensively in the main text.
6) That means you also need to summarize the nonparm results for the other 3 bivariate systems in Table 2. How to do this? Maybe put the cor results only, for Spearman only (or Kendall, not sure which to choose) into Table 2.  
7) Probably ought to combine tables S6, S8, S10 into one table, and fix it so
whenever we currently cite one of those, change it so we cite the combined table instead.
8) The nonparam stats are not estimators of tail dependence, they measure 
something else (though related). Make it clear we know this. It turns out there are estimators
of tail dependence. Do we want to mention that?
-->

@@

<!--Display model selection results for soilCN data in a table-->
```{r tab_soilCNfit, echo=F, results="asis"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
BivMS_res_Loecke<-readRDS("./Results/fitting_results/BivMS_soilCN.RDS")
h<-BivMS_res_Loecke$InfCritRes[,c("copname","AIC","AICw","BIC","BICw","LTdep","UTdep")]
colnames(h)<-c("Copula","AIC","AICw","BIC","BICw","LT","UT")
h_ord <- h[order(h$AIC),] #sorting data: min AIC to max AIC

#---- This line forces the formating which is not always true by using digits arg in kable function ----
h_ord$AIC<-formatC(h_ord$AIC,2,format="f")
h_ord$AICw<-formatC(h_ord$AICw,2,format="f")
h_ord$BIC<-formatC(h_ord$BIC,2,format="f")
h_ord$BICw<-formatC(h_ord$BICw,2,format="f")
h_ord$LT<-formatC(h_ord$LT,4,format="f")
h_ord$UT<-formatC(h_ord$UT,4,format="f")
#-------------------------------------------------

knitr::kable(h_ord, #longtable = T, 
             format = "latex",linesep = "",row.names = F, #digits = c(4,2,2,2,2,4,4), 
      caption.short = "Model fitting results for soil C and N dataset",
      caption = "Model fitting results for soil C and N dataset using 16 copula families: normal (N), Frank (F), Clayton (C), survival Clayton (SC), Gumbel (G), survival Gumbel (SG), Joe (J), survival Joe (SJ), BB1, survival BB1 (SBB1), BB6, survival BB6 (SBB6), BB7, survival BB7 (SBB7), BB8, survival BB8 (SBB8). Copulas are sorted according to their AIC values (2nd column). AICw = AIC weight; BIC = BIC value; BICw = BIC weight; LT = the lower-tail dependence statistic for the indicated copula family, with fitted parameters; UT = the same for upper-tail dependence. AIC, BIC and their corresponding weights are rounded upto 2 decimal place whereas tail dependences are rounded upto 4 decimal places. \\label{tab_soilCNfit}",
      booktabs = TRUE)
```

### 2019-09-22 SupportingInformation.Rmd
copula abbreviation added in table caption

<!--Display model selection results for BMR:birds data in a table-->
```{r tab_bmr_birds_fit, echo=F, results='markup'}
h<-BivMS_birds$InfCritRes[,c("copname","AIC","AICw","BIC","BICw","LTdep","UTdep")]
colnames(h)<-c("copula","AIC","AICw","BIC","BICw","LT","UT")
h_ord <- h[order(h$AIC),] #sorting data: min AIC to max AIC
knitr::kable(h_ord,
             format='latex',linesep = "",row.names = F, digits = c(4,2,2,4,4),
             caption.short = "Model fitting results for the bird body mass and BMR dataset",
             caption = "Results of fitting our 16 copula families to the bird body mass and BMR dataset. Analogous to Fig. \\ref{MT-tab_soilCNfit}, see caption of that figure for details. \\label{tab_bmr_birds_fit}",
             booktabs=T)
```

@@

<!--Display model selection results for BMR:mammals data in a table-->
```{r tab_bmr_mammals_fit, echo=F, results='markup'}
h<-BivMS_mammals$InfCritRes[,c("copname","AIC","AICw","BIC","BICw","LTdep","UTdep")]
colnames(h)<-c("copula","AIC","AICw","BIC","BICw","LT","UT")
h_ord <- h[order(h$AIC),] #sorting data: min AIC to max AIC
knitr::kable(h_ord,
             format='latex',linesep = "",row.names = F, digits = c(4,2,2,4,4),
             caption.short = "Model fitting results for the mammal body mass and BMR dataset",
             caption = "Results of fitting our 16 copula families to the mammal body mass and BMR dataset. Analogous to Fig. \\ref{MT-tab_soilCNfit}, see caption of that figure for details. \\label{tab_bmr_mammals_fit}",
             booktabs=T)
```

@@

<!--Display model selection results for Cedar-creek data for year 2000 in a table-->
```{r tab_cc2000fit, echo=F, results='markup'}
h<-BivMS_res_cc$`2000`$InfCritRes[,c("copname","AIC","AICw","BIC","BICw","LTdep","UTdep")]
colnames(h)<-c("copula","AIC","AICw","BIC","BICw","LT","UT")
h_ord <- h[order(h$AIC),] #sorting data: min AIC to max AIC
knitr::kable(h_ord,
             format='latex',linesep = "",row.names = F, digits = c(4,2,2,4,4),
             caption.short = "Model fitting results for the Cedar Creek dataset",
             caption = "Results of fitting our 16 copula families to the Cedar Creek dataset, year 2000. Analogous to Fig. \\ref{MT-tab_soilCNfit}, see caption of that figure for details. \\label{tab_cc2000fit}",
             booktabs=T)
```

@@

<!--table for Best-fitting copulas, green spruce aphid abundance data-->
```{r tab_count_bestcop, echo=F, results="markup"}
#library(dplyr)
#knitr::opts_knit$set(kable.force.latex = TRUE)
knitr::kable(RES_aphid_count$info_ord_copname[,,1], #longtable = T,
             format='latex',linesep = "",
             caption.short = "Best-fitting copulas, green spruce aphid abundance data",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for green spruce aphid abundance data. Copulas 
considered were the normal, Clayton, Gumbel, Frank, Joe, BB1, BB6, BB7, BB8, survival Clayton, survival Gumbel, 
survival Joe, survival BB1, survival BB6, survival BB7, and survival BB8 copulas, with abbreviations in the methods for Q1. NA occurs along the diagonal of the matrix because the diagonal represents a sampling location compared to itself.\\label{tab_count_bestcop}",
             booktabs=TRUE
             )#%>% # only with 'latex'/'html' format
 # kableExtra::kable_styling(latex_options = c("striped","HOLD_position"))
```

@@

<!--table for Best-fitting copulas, leaf plum curling aphid first flight data-->
```{r tab_ff_bestcop, echo=F, results="markup"}
knitr::kable(RES_aphid_ff$info_ord_copname[,,1], #longtable = T,
             format='latex',linesep = "",
             caption.short = "Best-fitting copulas, leaf-curling plum aphid first flight data",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for leaf-curling plum aphid first flight data. Copulas considered were as in Table \\ref{tab_count_bestcop}, with abbreviations in the methods for Q1. NA occurs along the diagonal of the matrix because the diagonal represents a sampling location compared to itself.  \\label{tab_ff_bestcop}",
             booktabs=TRUE
             )
```

@@

<!--table for Best-fitting copulas, Ceratium furca abundance data-->
```{r tab_pns_bestcop, echo=F, results="markup"}
knitr::kable(RES_plankton_north_sea$info_ord_copname[,,1], #longtable=T,
             format='latex', linesep = "",
             caption.short = "Best-fitting copulas, \\textit{Ceratium furca} abundance data",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for \\textit{Ceratium furca} abundance data. See methods for Q1 for copula abbreviations. Indep.=Independent. NA occurs along the diagonal because diagonal entries represent a sampling location compared to itself.\\label{tab_pns_bestcop}",
             booktabs=TRUE
             )
```

@@

<!--table for Best-fitting copulas, methane-flux data-->
```{r tab_methane_bestcop, echo=F, results="markup"}
knitr::kable(RES_methane$info_ord_copname[,,1], #longtable=T,
             format='latex',linesep = "",
             caption.short = "Best-fitting copulas, methane-flux data",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for methane-flux data. See methods for Q1 for copula abbreviations. Indep.=Independent. NA occurs along the diagonal because diagonal entries represent a sampling location compared to itself.\\label{tab_methane_bestcop}",
             booktabs=TRUE
             )
```

>>>>

<!--Display model selection results for BMR:birds data in a table-->
```{r tab_bmr_birds_fit, echo=F, results='markup'}
h<-BivMS_birds$InfCritRes[,c("copname","AIC","AICw","BIC","BICw","LTdep","UTdep")]
colnames(h)<-c("Copula","AIC","AICw","BIC","BICw","LT","UT")
h_ord <- h[order(h$AIC),] #sorting data: min AIC to max AIC

#---- This line forces the formating which is not always true by using digits arg in kable function ----
h_ord$AIC<-formatC(h_ord$AIC,2,format="f")
h_ord$AICw<-formatC(h_ord$AICw,2,format="f")
h_ord$BIC<-formatC(h_ord$BIC,2,format="f")
h_ord$BICw<-formatC(h_ord$BICw,2,format="f")
h_ord$LT<-formatC(h_ord$LT,4,format="f")
h_ord$UT<-formatC(h_ord$UT,4,format="f")
#-------------------------------------------------

knitr::kable(h_ord,
             format='latex',linesep = "",row.names = F, #digits = c(4,2,2,2,2,4,4),
             caption.short = "Model fitting results for the bird body mass and BMR dataset",
             caption = "Results of fitting our 16 copula families to the bird body mass and BMR dataset. Analogous to Fig. \\ref{MT-tab_soilCNfit}, see caption of that figure for details. \\label{tab_bmr_birds_fit}",
             booktabs=T)
```

@@

<!--Display model selection results for BMR:mammals data in a table-->
```{r tab_bmr_mammals_fit, echo=F, results='markup'}
h<-BivMS_mammals$InfCritRes[,c("copname","AIC","AICw","BIC","BICw","LTdep","UTdep")]
colnames(h)<-c("Copula","AIC","AICw","BIC","BICw","LT","UT")
h_ord <- h[order(h$AIC),] #sorting data: min AIC to max AIC

#---- This line forces the formating which is not always true by using digits arg in kable function ----
h_ord$AIC<-formatC(h_ord$AIC,2,format="f")
h_ord$AICw<-formatC(h_ord$AICw,2,format="f")
h_ord$BIC<-formatC(h_ord$BIC,2,format="f")
h_ord$BICw<-formatC(h_ord$BICw,2,format="f")
h_ord$LT<-formatC(h_ord$LT,4,format="f")
h_ord$UT<-formatC(h_ord$UT,4,format="f")
#-------------------------------------------------

knitr::kable(h_ord,
             format='latex',linesep = "",row.names = F, #digits = c(4,2,2,2,2,4,4),
             caption.short = "Model fitting results for the mammal body mass and BMR dataset",
             caption = "Results of fitting our 16 copula families to the mammal body mass and BMR dataset. Analogous to Fig. \\ref{MT-tab_soilCNfit}, see caption of that figure for details. \\label{tab_bmr_mammals_fit}",
             booktabs=T)
```

@@

<!--Display model selection results for Cedar-creek data for year 2000 in a table-->
```{r tab_cc2000fit, echo=F, results='markup'}
h<-BivMS_res_cc$`2000`$InfCritRes[,c("copname","AIC","AICw","BIC","BICw","LTdep","UTdep")]
colnames(h)<-c("Copula","AIC","AICw","BIC","BICw","LT","UT")
h_ord <- h[order(h$AIC),] #sorting data: min AIC to max AIC

#---- This line forces the formating which is not always true by using digits arg in kable function ----
h_ord$AIC<-formatC(h_ord$AIC,2,format="f")
h_ord$AICw<-formatC(h_ord$AICw,2,format="f")
h_ord$BIC<-formatC(h_ord$BIC,2,format="f")
h_ord$BICw<-formatC(h_ord$BICw,2,format="f")
h_ord$LT<-formatC(h_ord$LT,4,format="f")
h_ord$UT<-formatC(h_ord$UT,4,format="f")
#-------------------------------------------------

knitr::kable(h_ord,
             format='latex',linesep = "",row.names = F, #digits = c(4,2,2,2,2,4,4),
             caption.short = "Model fitting results for the Cedar Creek dataset",
             caption = "Results of fitting our 16 copula families to the Cedar Creek dataset, year 2000. Analogous to Fig. \\ref{MT-tab_soilCNfit}, see caption of that figure for details. \\label{tab_cc2000fit}",
             booktabs=T)
```

@@

<!--table for Best-fitting copulas, green spruce aphid abundance data-->
```{r tab_count_bestcop, echo=F, results="markup"}
#library(dplyr)
#knitr::opts_knit$set(kable.force.latex = TRUE)
knitr::kable(RES_aphid_count$info_ord_copname[,,1], #longtable = T,
             format='latex',linesep = "",
             caption.short = "Best-fitting copulas, green spruce aphid abundance data",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for green spruce aphid abundance data. Copulas considered were the normal (N), Clayton (C), Gumbel (G), Frank (F), Joe (J), BB1, BB6, BB7, BB8, survival Clayton (SC), survival Gumbel (SG), survival Joe (SJ), survival BB1 (SBB1), survival BB6 (SBB6), survival BB7 (SBB7), and survival BB8 (SBB8) copulas. NA occurs along the diagonal of the matrix because the diagonal represents a sampling location compared to itself.\\label{tab_count_bestcop}",
             booktabs=TRUE
             )#%>% # only with 'latex'/'html' format
 # kableExtra::kable_styling(latex_options = c("striped","HOLD_position"))
```

@@

<!--table for Best-fitting copulas, leaf plum curling aphid first flight data-->
```{r tab_ff_bestcop, echo=F, results="markup"}
knitr::kable(RES_aphid_ff$info_ord_copname[,,1], #longtable = T,
             format='latex',linesep = "",
             caption.short = "Best-fitting copulas, leaf-curling plum aphid first flight data",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for leaf-curling plum aphid first flight data. Copulas considered were as in Table \\ref{tab_count_bestcop}. NA occurs along the diagonal of the matrix because the diagonal represents a sampling location compared to itself.  \\label{tab_ff_bestcop}",
             booktabs=TRUE
             )
```

@@

<!--table for Best-fitting copulas, Ceratium furca abundance data-->
```{r tab_pns_bestcop, echo=F, results="markup"}
knitr::kable(RES_plankton_north_sea$info_ord_copname[,,1], #longtable=T,
             format='latex', linesep = "",
             caption.short = "Best-fitting copulas, \\textit{Ceratium furca} abundance data",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for \\textit{Ceratium furca} abundance data. Copula families were considered as in Table \\ref{tab_count_bestcop}. Indep.=Independent. NA occurs along the diagonal because diagonal entries represent a sampling location compared to itself.\\label{tab_pns_bestcop}",
             booktabs=TRUE
             )
```

@@

<!--table for Best-fitting copulas, methane-flux data-->
```{r tab_methane_bestcop, echo=F, results="markup"}
knitr::kable(RES_methane$info_ord_copname[,,1], #longtable=T,
             format='latex',linesep = "",
             caption.short = "Best-fitting copulas, methane-flux data",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for methane-flux data. Copula families were considered as in Table \\ref{tab_count_bestcop}. Indep.=Independent. NA occurs along the diagonal because diagonal entries represent a sampling location compared to itself.\\label{tab_methane_bestcop}",
             booktabs=TRUE
             )
```
